Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-07-02 paper/main.tex
revision until results

\ref{tab:descr-nouns}) were pooled into 11 new categories (sex\_f; sex\_m; fahead; object).

@@

\paragraph{audio stimulus: contrasts of parameter estimate}
\todo[inline]{Warum ist welche COPES so gemacht und warum COPE 1 die Nummer 1}
% wieso, weshalb, warum
We created $t$-contrasts\dots
% table reference
See Table \ref{tab:ao-contrasts}

\begin{table*}[t]
\caption{Contrasts of parameter estimates for the analysis of the audio-only
    stimulus (AO).
\texttt{all non-geo} = all non-geo related regressors except furniture.}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrasted} & \textbf{aim/goal} \\
\midrule
1 & geo, groom > all non-geo & PPA \tabularnewline
2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
3 & room, se\_new, se\_old > all non-geo & PPA \tabularnewline
4 & geo > all non-geo & PPA \tabularnewline
5 & groom > all non-geo & PPA \tabularnewline
6 & se\_new > all non-geo & PPA \tabularnewline
7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
8 & se\_new > se\_old & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

\paragraph{audio-visual stimulus: contrasts of parameter estimate}
% wieso, weshalb, warum
We created a contrast presumably correlating with increased hemodynamic activity
in the PPA by contrasting different kind of cuts, noteably without controlling
for the specific visual content depicted in the frame after each cut.
% cinematographic rationale
The cinematographic rationale was that - over the course of a movie - cuts shift
from establishing the setting and the spatial relationships within a setting at
the beginning of a movie to depicting persons and objects more relevant to the
subsequently evolved narrative later in the movie {brown2012cinematography;
mercado2011filmmakers}.
% neuroscientific rationale
The neurocientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes resp. view-points
\citep{epstein1999parahippocampal}.
% im Ergebnis
Hence, we contrasted cuts to a setting occurring for the first time (vse\_new)
and cuts within a locale depicted for the first time (vpe\_new) with shots to a
recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).

\begin{table*}[t]
    \caption{Contrasts of parameter estimates for the analysis of the audio-visual movie (AV).}
\label{tab:av-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrasted} & \textbf{aim/goal} \\
\midrule
1 & vse\_new > vpe\_old  & PPA \tabularnewline
2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
3 & vse\_new > vse\_old & PPA \tabularnewline
4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
6 & vno\_cut > vse\_new & negative control \tabularnewline
7 & vno\_cut > vse\_old & negative control \tabularnewline
8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
10 & se\_new > se\_old & control for narrator \tabularnewline
\end{tabular}
\end{table*}

\paragraph{Registration \& smoothing: individuals vs. group}

\todo[inline]{Wie immer bei Co-Registration: bitte prüfen, ob ich es richtig
geschrieben habe}

\todo[inline]{wie besprochen sind die individuelle Results im
subject space und werden erst später für die Bland-Altman-Plots nach MNI
transformiert}

% anatomical alignment of single subjects
The GLM analysis that fitted each voxel's time course separately for each
subject was performed in functional space preserving the orientation of the EPI
images. For subsequent subject-specific second level results, subject-specific
BOLD T2* time series were anatomically aligned via linear transformation to a
subject-specific, study-specific T2* template (s.
\href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
that served as standard space.
% anatomical alignment for group results
For subsequent the third level results averaging contrasts of interest across
subjects, time series were anatomically aligned via non-linear transformation
[+++wie genau?+++] to a
\href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific
T2* group template}.
% MNI co-registration
To facilitate visualization and identification of cortical structures, this
reference images was later co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom)

\subsubsection{second level}
% model
The second-level analyses which averaged contrast estimates over the eight
stimulus segments were carried out using a fixed effects model by forcing the
random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
Effects; \citep{beckmann2003general, woolrich2004multilevel}.
% thresholding
(Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>2.3 and a (corrected) cluster significance threshold of p=.05
\citep{worsley2001statistical}.

\subsubsection{third level}
% model
Third level analyses which averaged contrast estimates over subjects were
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Z (Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a (corrected) cluster significance threshold of p=.05
\citep{worsley2001statistical}.
% brain region identification
Brain regions associated with observed clusters were determined with the Juelich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
PPA ROI masks for individual subjects and a PPA group overlap mask were created
from data provided by \citep{sengupta2016extension}.

\subsection{Erstellung der Masken, spatial transformations}

\subsubsection{plot-group-and-individuals.py}

\subsubsection{plot-bland-altman.py}

% generate-masks.py; DO NOT TOUCH!
% FOR GROUP:
% 0. In FSLeyes, manually created probabilistic brain lobe maps from \href{"https://doi.org/10.5281/zenodo.1470761"}{the MNI Structural Atlas} (./data/atlases/mni_prob_*.nii.gz)
% 1. these brain lobe maps were aligned (via FSL's flirt -applyxf with 12 dof) to the \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific T2* group template} (./data/atlases/grpbold3Tp2_mni_prob_*.nii.gz)
% 2. from \href{"https://github.com/psychoinformatics-de/studyforrest-data-visualrois"} {sengupta2016extension}: UNIlateral probabilistic group ROI masks (data/masks/*_overlap.nii.gz) -> BIlateral probabilistic & binary grp ROI masks in grp space (.data/masks/bilat_???_prob.nii & .data/masks/bilat_???_binary.nii )
% FOR SUBJECTS:
% 1. bilateral grp ROI masks in grp space -> bilateral grp ROI masks in subject space (applywarp; sub-??/masks/grp_*_bin.nii.gz)
% 2. probabilistic MNI mask -> subject space (via FSL's applywarp)
% 3. merge probabilistic occipital & temporal mask in subject space
%	(sub-??/masks/mni_prob_occip_tempo.nii.gz)
% 4. created subject-specific FOV from 4d 7t audio drama time series
%	(./sub-??/masks/ao_fov_mask.nii.gz)
% 5. individual, unilateral ROIs from {sengupta2016extension} were joined and co-registered to MNI 152 (1mm) space, and binarized
% 6. individual (un)thresholded zmaps (from the COPEs) were co-regi<wstered with MNI 152 (1mm) template.

@@

>>>>

\ref{tab:descr-nouns-rules}) were pooled into 11 new categories (sex\_f; sex\_m; fahead; object).

@@

\paragraph{AO: COPEs}

\todo[inline]{Why done this way? Why is no. 1 the one?}
% intro
For the AO stimulus, we created eight $t$-contrasts that aimed to isolate the PPA and five contrasts
for negative control purposes (see Table \ref{tab:ao-contrasts}).
% PPA contrasts
Contrasts 6-8: words belonging to the categories \texttt{se\_new} and
\texttt{se\_old} were very vague in describing a scene compared to the richness
of a picture. Hence, we assumed smaller probability of successfully isolating
the PPA (+ recht geringe Anzahl verglichen mit geo, groom) (<- das kommt eher in
Discussion der Kontraste/Ergebnisse).
% furniture: blurred border between groom and object
Furniture was not included in one of the contrast because it can be considered
as an object or geometry-defining structure of a room.

% negative control contrasts
Contrasts 9-13 correspond to the contrasts 1-5 of the AV stimulus and served as
negative controls because increased activation in the PPA could also be
correlated with moment of cuts and a possible change in the soundscape of a
scene.

\begin{table*}[t]
    \caption{Contrasts of parameter estimates for the analysis of
        the audio-only stimulus (AO).
\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m). Contrast
1-8 aim to isolate the PPA.
Contrast 9-13 serve as negative control at the moments of movie cuts
with possible changes of the audio tracks soundscape (see Table \ref{tab:av-contrasts}}

\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > all non-geo & PPA \tabularnewline
2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
3 & gro
om, se\_new, se\_old > all non-geo & PPA \tabularnewline
4 & geo > all non-geo & PPA \tabularnewline
5 & groom > all non-geo & PPA \tabularnewline
6 & se\_new > all non-geo & PPA \tabularnewline
7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
8 & se\_new > se\_old & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

\paragraph{AV: COPEs}

\todo[inline]{change stability of contrast plot from 6 to 5 COPES (line 40 in
script)}

\todo[inline]{Why done this way? Why is no. 1 the one?}
% intro
For the AV stimulus, we created five contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind of cuts.
and five contrasts for negative control purposes.
% no control for frames content
Notably, this was done without an annotation of the visual content depicted in
the frame after each cut and statistically controlling confounding variables.
% cinematographic rationale
The cinematographic rationale was that movie tend to establishing the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie. Later in the movie, the field
sizes of movie shots tend to decrease when switching back to already established
settings (\texttt{vse\_old}). Shots within a recurring settings tend to shift to
depicting persons and objects (\texttt{vpe\_old}) more relevant to the evolved
narrative \citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that simply that activity in the PPA is
greater when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% im Ergebnis
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.

\begin{table*}[t]
    \caption{Contrasts of parameter estimates for the analysis of the audio-visual movie (AV).}
\label{tab:av-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & vse\_new > vpe\_old  & PPA \tabularnewline
2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
3 & vse\_new > vse\_old & PPA \tabularnewline
4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
6 & vno\_cut > vse\_new & negative control \tabularnewline
7 & vno\_cut > vse\_old & negative control \tabularnewline
8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
10 & se\_new > se\_old & control for narrator \tabularnewline
\end{tabular}
\end{table*}

\paragraph{second level (+ alignment)}
% single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject was performed in functional space preserving the orientation of the EPI
images.
% two ways of co-registration
For subsequent second level results, we co-registered the subjects in two ways.
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
On the one hand, subject-specific BOLD T1* time series were anatomically aligned
via linear transformation to a subject-specific, study-specific T1* template
that served as standard space.
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
On the other hand, time series were aligned via non-linear transformation to a
study-specific T2* group template.
% MNI152
This reference images was later co-registered to the MNI 152 template with an
affine transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures,

\subsubsection{second level}
% model
The second level analyses which averaged contrast estimates over the eight
stimulus segments were carried out using a fixed effects model by forcing the
random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
Effects; \citep{beckmann2003general, woolrich2004multilevel}.
% thresholding (Z>2.3 in subject-space; Z>3.4 in group space)
(Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a (corrected) cluster significance threshold of p=.05
\citep{worsley2001statistical}.

\subsubsection{third level}
% model
The third level analysis which averaged contrast estimates over subjects were
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Z (Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a (corrected) cluster significance threshold of p=.05
\citep{worsley2001statistical}.

% brain region identification
Brain regions associated with observed clusters were determined with the Juelich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
PPA ROI masks for individual subjects and a PPA group mask of individual PPAs overlapping were created from data provided by \citep{sengupta2016extension}.

@@

% Unterschiedliche Qualität der Kontrast
% Warum wurde Kontrast 1 als Kontrast 1 gewählt; se\_new se\_old sind recht
% vague in der Beschreibung der Szene verglichen mit Bild; Anzahl der Events
% ergibt auch noch Sinn;
